% ABSTRACT
For a long time, cameras have been power hungry, and this was doubly so, compounded by their complexity, requiring power-hungry processors to capture incoming data.  However, significant advances in low-power technology will soon make these concerns a thing of the past.  We lay out the low-power landscape and argue that conditions are ripe for low power, wearable cameras today.  Glasses.  With glasses we can see the eye and we can see what the eye can see.  We highlight state of the art and trends in low-power hardware showing that low-power context-aware eyeglasses will be viable soon, and present the challenges remaining.  Finally, we demonstrate a prototype, a pair of wireless eyeglasses containing two cameras.  Combining photo data from a front-facing scene camera and an inward-facing eye camera, our system uses machine learning to predict the users gaze.  We show that our glasses prototype, which was built using low-power COTS parts, can be used to track the wearer's gaze with reasonable accuracy.


%For a long time, cameras have been power hungry, and this was doubly so,
%compounded by their complexity, requiring power-hungry processors to capture
%incoming data.  However, significant advances in low-power technology will
%soon make these concerns a thing of the past.  We lay out the low-power
%landscape and argue that conditions are ripe for low power, wearable cameras
%today.  Glasses.  With glasses we can see the eye and we can see what the eye
%can see.  We highlight state of the art and trends in low-power hardware
%showing that low-power context-aware eyeglasses will be viable soon, and
%present the challenges remaining.  Finally, we demonstrate a prototype, a pair
%of wireless eyeglasses containing two cameras.  Combining photo data from a
%front-facing scene camera and an inward-facing eye camera, our system uses
%machine learning to predict the users gaze.  We show that our glasses
%prototype, which was built using low-power COTS parts, can be used to track
%the wearer's gaze with reasonable accuracy.
