\section{Background}
\label{sec:background}

Cameras are becoming near ubiquitous in modern society.  Today, they are found in shops, on traffic lights, in schools, in the pocket of almost every cellphone carrying person, and even, increasingly, in our homes.  Thanks in large part to advancing technologies and falling costs, cameras are everywhere.  And, while the average person on the street is aware that cameras are all around capturing pictures and video, what they are not aware of is that there are a whole host of smart cameras, which turn visual data about some knowledge of the world.

Smart cameras, perhaps better called vision sensors than camreas, are cameras which extract some information fro visual data.  Long at the heart of cutting edge manufacturing techniques, these so called smart cameras using vision processing and machine learning techniques to extract context from or apply labels to visial data.  Increasingly, smart cameras are being employed in more dynamic environments in tasks such as counting bodies or vehicles and even facial recognition.

% FIXME cite the mental illnesses thing
Another purpose of smart cameras is to glean information from peoples' eyes.  By tracking the movement of the eyes, cameras can glean information about the person who the eyes belong to, such as that he or she is sleepy or not paying attention or drunk.  Eye tracking can even be used to detect and treat mental disorders such as Schizophrenia \cite{schizo-abnormalities}.  In addition to eye tracking, cameras can peform gaze tracking, which combines information from an image of the eye with an image of the scene within the field of vision to identify where the eye is looking.

% FIXME Dikablis cost?
Commercial eye and gaze tracking headgear exists, but such systems are expensive, can be bulky and are often inelegant.  Examples of current eye tracking headgead are the Ergoneers Dikablis and the ASL Mobile Eye-XG.  The Mobile Eye-XG is a wired system and the Dikablis glasses use a proprietary wireless interface which requires running special software for interaction with the glasses.

%gaze tracking has many applications
%- find x,y,z

%today done in <foo> settings
% - lab environments
% - elswehere
% - pros/cons/ etc of these
%   + size, cost, calibration



% cameras are near ubiquitous

% what the general public at large has yet to grasp is that cameras are no longer capturing images, but actually processing data.  These "smart cameras" have yet to make their way into the public's awareness.

% what can we do with smaryt cameras on the eyes of the wearer?  intoxication or drowsy driving detection.  psycho evaluation.  accessability computing device for the disabled.

% existing eye tracking headgear.

% where they lack

\subsection{Related Work}

