\section{Introduction}
\label{sec:intro}

It has been said since biblical times that ``the eye is the window to the
soul''. In modern computing, however, the eye remains a one-way mirror,
accepting input from the world but providing no insight to the world
interacting with it. With the development of the InSight platform, we seek to
rectify this imbalance, building an efficient, wireless, full-day,
comfortable gaze tracking system.

Gaze tracking enables a diverse array of applications. It allows for targeted
advertisements that can change content depending on who is looking at them as
well as establishing an authoritative count of impressions. Gaze tracking
provides a powerful diagnostic medium for the detection of diseases such as
schizophrenia or more immediate measures such as intoxication. Advanced,
high-precision gaze tracking even allows for instantaneous dynamic lens
adaptation. Combined with advances in materials science, glasses that
automatically adapt to the current wearer enter the realm of possibility.

{\em Efficient.} Leveraging previous work~\cite{gaze-neural-net, others?}, we
perform a short (order of 5 minute) training session to develop a neural net
that is loaded onto the glasses. This enables real-time gaze tracking on a
low-power microcontroller, with a reasonable degree of accuracy.

{\em Wireless.} Our system includes a bluetooth communication
component that enables real-time communication of user focus. Currently this
is communicated only to a prototype Android application, however the system
could easily be extended to communicate with local advertisements. For
advertisements with a specialized embedded QR-code, a look at the
advertisement can generate a positive viewed impression to the advertiser,
including duration of focus and number of impressions.

{\em Comfortable.} To fully realize our vision, the gaze-tracking system needs to
be as natural to the wearer as a regular pair of glasses. This necessitates a
small, compact form factor both for the sense hardware (2x cameras) and the
energy storage (lightweight battery). Our complete prototype system (cameras,
PCB, plastic enclosure, frames, wires, battery) weighs in at 85~g, barely 3.5
times the weight of traditional glasses\footnote{Estimated from a small survey
of author's glasses}.

{\em Full-Day.} In addition to comfort, an always-on gaze tracking system must
be sufficiently power efficient to run for an entire day. The InSight glasses
are duty cycled, evaluating gaze every XXX~s at a cost of XXX~mJ per
measurement. Powered off of our 8.8~g, 600~mAh battery this allows the InSight
system to run for XXX~hours continuously.

